---
output: github_document
always_allow_html: yes
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

# headliner

<!-- badges: start -->
[![License: MIT](https://img.shields.io/github/license/mashape/apistatus.svg)](https://github.com/zambujo/headliner/blob/master/LICENSE)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.org/zambujo/headliner.svg?branch=master)](https://travis-ci.org/zambujo/headliner)
[![R build status](https://github.com/zambujo/headliner/workflows/R-CMD-check/badge.svg)](https://github.com/zambujo/headliner/actions)
![pkgdown](https://github.com/zambujo/headliner/workflows/pkgdown/badge.svg)
![knit README](https://github.com/zambujo/headliner/workflows/Render%20README/badge.svg)
<!-- badges: end -->


`headliner` is a package to publish headlines' data.  In other words, it provides a static generator for headlines.  `headliner` is ideal to quickly publish and distribute RSS feeds, for instance.


## Installation

The package is not yet on CRAN.

You can install the development version of `headliner` from github using:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("zambujo/headliner")
```

## Example

Use this example to publish the contents of a data frame:

```{r example, eval=FALSE}
library(headliner)
data(sciencegeist)

sciencegeist <- head(sciencegeist)
build_hd(sciencegeist, 
         title = "Sciencegeist newest posts", 
         save_as = "headlines.html")
```
